Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
add screenshot

@@

@@

\subsubsection{Facet}
The user can perform faceting when there is one selected view from the working
area. When clicking “FACET”, a popup window will show prompting the user to select,
for each repeating direction (row or column or both), a field and its type to facet.
Note that facetting will be applied to all inner views of the operand. Due to our time
constraints, selecting a subset of inner views to only perform facet on the set of
inner views is unavailable right now.

\paragraph{Validation} Since parameters for facet are fields, facetting
depends on the dataset. Thus, “FACET” button will show a warning signal when the
operand has multiple data source. For instance, selecting a concat view that
contains a chart from cars dataset and population dataset will result in having
the warning signal in the “FACET”  button.

@@

@@

@@

The key result for Pleiades was how easy it became to compose graph. 
During our presentation, we asked a lot of our peers to try out our 
application and compare their workflow to that when they used the 
Vega-Lite API along with a JSON spec. The results were as we expected: Pleiades 
gives a better understanding and ease at composing different charts and see
what fits the best. The key-idea behind why Pleiades makes composing charts 
easier and more intuitive is because the process is bottom-up, 
whereas Vega-lite is top-down. Also, the graphical user interface 
provided used with a smother way to compose charts, than to write nested JSON specs.

One more results that we found was, having the ability to perform 
the four operations: Layer, Concat, Facet and Repeat, it gave the user
a better understanding of these operations and how to properly use then. 
he validation steps, along with the error message that Pleiades provides 
helps users to understand what they are doing wrong, helping them in their 
education about visualization in general.

In terms of exploring data, the time it takes to compose different 
charts and see find useful results, went down by a lot because of the 
high-level of interactivity provided. Users don’t have to worry about 
updating JSON code for every small change in their chart.

Overall, Pleiades resulted in easing beginners to develop composite 
charts, save time for users, ease data-exploration, and act as a 
support toolkit for education.

>>>>

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{replace.png}
 \caption{Before and after replacing the selcted bar chart with the selected scatter plot}
\end{figure}

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{layer.png}
 \caption{Before and after layering the selcted error-band chart with the selected scatter plot}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{layer_warn.png}
 \caption{Warning when axes of layering views are not fully compatible (between the bar chart and the scatter plot)}
\end{figure}

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{concat.png}
 \caption{Before and after concatenating the selcted bar chart with the selected scatter plot}
\end{figure}

\subsubsection{Facet}
The user can perform faceting when there is one selected view from the working
area. When clicking “FACET”, a popup window will show prompting the user to select,
for each repeating direction (row or column or both), a field and its type to facet.
Note that facet-ing will be applied to all inner views of the operand. Due to our time
constraints, selecting a subset of inner views to only perform facet on the set of
inner views is unavailable right now.

\paragraph{Validation} Since parameters for facet are fields, facet-ing
depends on the dataset. Thus, “FACET” button will show a warning signal when the
operand has multiple data source. For instance, selecting a concat view that
contains a chart from cars dataset and population dataset will result in having
the warning signal in the “FACET”  button.

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{facet.png}
 \caption{Before and after facet-ing the selected scatter plot with ``Origin'' as the field for facet-ing column.}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{facet_warn.png}
 \caption{Warning on repeat and facet when not every dataset in the selected view are from the same source.}
\end{figure}

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{repeat.png}
 \caption{Before and after repeating the selected scatter plot with ``Displacement'' and ``Cylinders'' as the list of fields for repeat column on x-axis.}
\end{figure}

@@

result here
